Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
Fault results

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults  \\
	\hline
	Group A & 36 & 40 & 35 \\
	\hline
	Group B & 31 & 47 & 28 \\
	\hline
	\end{tabular}
	\caption{Fault counts of risk type per group}
\end{table}

@@

\subsection{Results for H\textsubscript{Fault}}

>>>>

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults  \\
	\hline
	Group A & 36 & 40 & 35 \\
	\hline
	Group B & 31 & 47 & 28 \\
	\hline
	\end{tabular}
	\caption{Fault frequency of risk type per group}
\end{table}

@@

\subsection{Results for H\textsubscript{Fault}}
As mentioned previously, the Chi-Square test of independence was used to determine if the reviewers discovered the same frequency of results. The result of the X\textsubscript{2} was 1.5998, generating a p-value of 0.4494. Thus, the null hypothesis H\textsubscript{0} Fault is rejected.
